Hydraulic bore interaction with a column - A comparison between the solution of the shallow equation and experimental results

### 2015-03-12 doc/paper/paper.tex
update paper.tex. add plots for wave height history measured at back face of column

%todo 
%there are some compiling problem when I try to compile the following 4 lines

@@

@@

\section{Dam Break with cylinder column}\label{Sec:Cylinder}
Figure \ref{fig:waveheight_cylinder_x=11.0} shows the time history of the wave height measured at $0.04m$ ahead of the front point of cylinder column($0.1m$ ahead of the center of the column).
%Since the way GeoClaw treat a cell partly belong to cylinder and partly belong to tank bottom is to give that cell an average value of topography from cylinder and tank bottom based on area ratio, we get a quasi-circle actually instead of circle. Thus the result in this case does not agree well with the experiment result. 
%Future test can be conducted by setting a higher level for mesh refinement to get a better circle.
Similar feature as in the square column case Figure \ref{fig:waveheight_square_x=11.0} can be found.
However, the wave height at the second peak in this case is almost the same as that in square column case (around $0.22m$ in both case), while this feature is quite different for the experimental results between the two cases.
\par
Note that diameter of the cylinder is equal to half the length of the square column. 
Thus in experiment, the square column can block the flow in in a more efficient way than cylinder does, since the cylinder has a smoother shape for the fluid to pass by. 
This explains why we see a lower peak of wave height as well as less steep curve for history of wave height in case with the cylinder in the experiment. 
In GeoClaw, a geometry is represented with quadrilateral cells. 
In the cylinder case, the cylinder is represented with square cells since our background mesh is simple structured quadrilateral mesh with square cells.
Based on this, we can deduce in GeoClaw, when the shock wave hits the cylinder, it is hitting onto many small faces vertical to flow direction at different locations. 
In other words, there is no cell which has a normal vector of front face pointing toward oblique direction other than the direction fluid comes.  
Thus it is similar to hitting onto one big face vertical to flow direction, which is the case with square column.  
This is why we get similar result in GeoClaw for case with square column and case with cylinder.
\begin{figure}[h!]
    \centering
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=1\textwidth]{./plots/waveheight_cylinder_x11}
        \caption{at x = 11}
        \label{fig:waveheight_cylinder_x=11.0}
    \end{subfigure}
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=1\textwidth]{./plots/waveheight_cylinder_x1104_largerTimeScale}
        \caption{at x = 11.04}
        \label{fig:waveheight_cylinder_x=11.04}
    \end{subfigure}
    \caption{time history of wave height for cylinder column case}
\end{figure}

>>>>

@@

Figure \ref{fig:waveheight_square_back} shows history of wave height measured at back face of the square column (at $X = 11.16$). Boundary layer detached near this region thus fluid in this region is difficult to be predicted. GeoClaw overestimates wave height in this region.  
    \includegraphics[width=0.4\textwidth]{./plots/waveheight_square_back}
    \caption{history of wave height measure at back face of the square column}
    \label{fig:waveheight_square_back}

@@

\section{Dam Break with cylinder column}\label{Sec:Cylinder}
Figure \ref{fig:waveheight_cylinder_x=11.0} shows the time history of the wave height measured at $0.04m$ ahead of the front point of cylinder column($0.1m$ ahead of the center of the column).
%Since the way GeoClaw treat a cell partly belong to cylinder and partly belong to tank bottom is to give that cell an average value of topography from cylinder and tank bottom based on area ratio, we get a quasi-circle actually instead of circle. Thus the result in this case does not agree well with the experiment result. 
%Future test can be conducted by setting a higher level for mesh refinement to get a better circle.
Similar feature as in the square column case Figure \ref{fig:waveheight_square_x=11.0} can be found.
However, the wave height at the second peak in this case is almost the same as that in square column case (around $0.22m$ in both case), while this feature is quite different for the experimental results between the two cases.
\par
Note that diameter of the cylinder is equal to half the length of the square column. 
Thus in experiment, the square column can block the flow in in a more efficient way than cylinder does, since the cylinder has a smoother shape for the fluid to pass by. 
This explains why we see a lower peak of wave height as well as less steep curve for history of wave height in case with the cylinder in the experiment. 
In GeoClaw, a geometry is represented with quadrilateral cells. 
In the cylinder case, the cylinder is represented with square cells since our background mesh is simple structured quadrilateral mesh with square cells.
Based on this, we can deduce in GeoClaw, when the shock wave hits the cylinder, it is hitting onto many small faces vertical to flow direction at different locations. 
In other words, there is no cell which has a normal vector of front face pointing toward oblique direction other than the direction fluid comes.  
Thus it is similar to hitting onto one big face vertical to flow direction, which is the case with square column.  
This is why we get similar result in GeoClaw for case with square column and case with cylinder.
\begin{figure}[h!]
    \centering
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=1\textwidth]{./plots/waveheight_cylinder_x11}
        \caption{at x = 11}
        \label{fig:waveheight_cylinder_x=11.0}
    \end{subfigure}
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=1\textwidth]{./plots/waveheight_cylinder_x1104_largerTimeScale}
        \caption{at x = 11.04}
        \label{fig:waveheight_cylinder_x=11.04}
    \end{subfigure}
    \caption{time history of wave height for cylinder column case}
\end{figure}
\par
Figure \ref{fig:waveheight_cylinder_back} shows history of wave height measured at back face of the cylinder column (at $X = 11.16$). 
GeoClaw gives a satisfied prediction in this region.
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.4\textwidth]{./plots/waveheight_cylinder_back}
    \caption{history of wave height measure at back face of the square column}
    \label{fig:waveheight_cylinder_back}
\end{figure}
